\newglossaryentry{benchmark harness} {
  name={benchmark harness},
  description={consists of multiple components which help to plan and control the execution of
benchmarks on multiple hosts, gather the results and store them for further
analysis.}
}

\newglossaryentry{benchmark} {
  name={benchmark},
  description={is a piece of software which runs on the system under test. It
produces load on the system and captures results of given metrics.}
}

\newglossaryentry{benchmark driver} {
  name={benchmark driver},
  description={is the interface between the \gls{benchmark controller} and
the \gls{benchmark}. It launches a given benchmark, captures the output and
extracts the results from the output.}
}

\newglossaryentry{benchmark controller} {
  name={benchmark controller},
  description={uses the \glspl{benchmark driver} to coordinate the execution of 
\glspl{benchmark} on the \glspl{system under test}.}
}

\newglossaryentry{system under test} {
  name={system under test},
  plural={systems under test},
  description={is the actual host or machine for which the benchmark results should
be generated.}
}

\newglossaryentry{independent variable} {
  name={independent variable},
  description={is also called an explanatory variable or input variable. It is a
variable whose values are set prior to the run of a benchmark. It includes all
factors which can possibly change the outcome of a benchmark.}
}

\newglossaryentry{dependent variable} {
  name={dependent variable},
  description={is a variable, whose values are generated during the run of a
benchmark. The values are dependent on the values of the \glspl{independent
variable}.}
}

\newglossaryentry{independent variable space} {
 name={independent variable space},
 description={is a set of independent variables and one or more values for each of
the variables.}
}

\newglossaryentry{experiment} {
  name={experiment},
  description={is a specification of one benchmark run defined by a value for
each of the \glspl{independent variable} needed and a \gls{system under test}
where the benchmark run should be executed on.}
}

\newglossaryentry{experiment series} {
 name={experiment series},
 plural={experiment series},
 description={is a term used in singular form for a set of experiments on a
system under test. The experiments are defined by a \gls{independent variable
space}.}
}

\newglossaryentry{experiment setup} {
  name={experiment setup},
  description={defines the overall experiment configuration. It contains an
\gls{experiment series} for each system under test which will be involved.}
 }
 
 \newglossaryentry{benchmark run} {
 name={benchmark run},
 description={A single execution of a \gls{benchmark} on one \gls{system under test}.}
 }
